Simulation Study: Informative Covariate (cubic)

### 2018-06-05 datasets/simulations/simulations-informative-cubic.Rmd
Rerun t-dist sims w/ ASH df specified

```{r t5-run-simulation}
if (file.exists(tdist_file)) {
    res <- readRDS(tdist_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = tdist_file)
}
```

@@

Since both `scott-empirical` and `scott-theoretical` are not appropriate when
the test statistics are not approximately normal, we also plot the results without
these methods.

```{r chisq4-metrics-averages-nofdrreg, results = "hide"}
plotsim_average(resdf, met = "rejections",
                filter_set = c(excludeSet, "scott-empirical", "scott-theoretical"),
                merge_ihw = TRUE, errorBars = TRUE)

plotsim_average(resdf, met = "FDR",
                filter_set = c(excludeSet, "scott-empirical", "scott-theoretical"),
                merge_ihw = TRUE, errorBars = TRUE)

plotsim_average(resdf, met = "TPR",
                filter_set = c(excludeSet, "scott-empirical", "scott-theoretical"),
                merge_ihw = TRUE, errorBars = TRUE)

plotsim_average(resdf, met = "TNR",
                filter_set = c(excludeSet, "scott-empirical", "scott-theoretical"),
                merge_ihw = TRUE, errorBars = TRUE) 
```

>>>>

For the t-distributed noise setting, we must specify the number of degrees of freedom
for ASH. We add an additional parameter to the `ashq` method with the corresponding
degrees of freedom of the noise distribution.

```{r}
bdplust <- modifyBMethod(bdplus, "ashq", df = 5)
```

We next run the simulations (including Scott's FDR Regression and ASH with degrees of
freedom specified).

```{r t5-run-simulation}
if (file.exists(tdist_file)) {
    res <- readRDS(tdist_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplust, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = tdist_file)
}
```

@@

Since `ashq` is not appropriate when the test statistics are not approximately normal or t,
we also plot the results without this method.

```{r chisq4-metrics-averages-noash, results = "hide"}
plotsim_average(resdf, met = "rejections", filter_set = c(excludeSet, "ashq"),
                merge_ihw = TRUE, errorBars = TRUE)

plotsim_average(resdf, met = "FDR", filter_set = c(excludeSet, "ashq"),
                merge_ihw = TRUE, errorBars = TRUE)

plotsim_average(resdf, met = "TPR", filter_set = c(excludeSet, "ashq"),
                merge_ihw = TRUE, errorBars = TRUE)

plotsim_average(resdf, met = "TNR", filter_set = c(excludeSet, "ashq"),
                merge_ihw = TRUE, errorBars = TRUE) 
```
